---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---


```{r, echo = FALSE, message=FALSE}
library(tidyverse)
library(readxl)
library(ggridges)
library(reshape2)
library(RColorBrewer)
library(scales)

options(dplyr.summarise.inform = FALSE)
```

```{r, warning=FALSE}
year = 2022
five_out_file_loc <- dir(paste0('C:\\Users\\brend\\Documents\\dev\\bss\\',year,'_study\\output\\fivemin'),
                    full.names = TRUE)
hour_out_file_loc <- dir(paste0('C:\\Users\\brend\\Documents\\dev\\bss\\',year,'_study\\output\\hourly'),
                    full.names = TRUE)
five_out_df <- do.call(rbind,lapply(five_out_file_loc,read.csv))
hour_out_df <- do.call(rbind,lapply(hour_out_file_loc,read.csv))

price_df <- read_excel('C:\\Users\\brend\\Documents\\dev\\bss\\2021_nodal_input.xlsx')
```

```{r}
getSeason <- function(DATES) {
    WS1 <- as.Date("2021-12-21", format = "%Y-%m-%d") # Winter Solstice 2021
    WS2 <- as.Date("2022-12-21", format = "%Y-%m-%d") # Winter Solstice 2022
    
    SE1 <- as.Date("2021-3-20",  format = "%Y-%m-%d") # Spring Equinox 2021
    SE2 <- as.Date("2022-3-20",  format = "%Y-%m-%d") # Spring Equinox 2022
    
    SS1 <- as.Date("2021-6-21",  format = "%Y-%m-%d") # Summer Solstice 2021
    SS2 <- as.Date("2022-6-21",  format = "%Y-%m-%d") # Summer Solstice 2022
    
    FE1 <- as.Date("2021-9-23",  format = "%Y-%m-%d") # Fall Equinox 2022
    FE2 <- as.Date("2022-9-23",  format = "%Y-%m-%d") # Fall Equinox 2022

    # Convert dates from any year to 2012 dates
    d <- as.Date(strftime(DATES, format="%Y-%m-%d"))
    yr <- year(DATES)
    
    ifelse(yr == 2021,
    ifelse (d >= WS1 | d < SE1, "Winter",
      ifelse (d >= SE1 & d < SS1, "Spring",
        ifelse (d >= SS1 & d < FE1, "Summer", "Fall"))),
    ifelse (d >= WS2 | d < SE2, "Winter",
      ifelse (d >= SE2 & d < SS2, "Spring",
        ifelse (d >= SS2 & d < FE2, "Summer", "Fall")))
    )
}
```



```{r}
five_out_df <- five_out_df %>% mutate(interval = '5-Minute')
hour_out_df <- hour_out_df %>% mutate(interval = 'Hourly')
out_df <- rbind(five_out_df,hour_out_df)
out_df %>%
  arrange(interval,date_time) %>%
  mutate(isDA = if_else(str_detect(product,'DA'), 'DA','not DA'))%>%
  mutate(date_time = ymd_hms(date_time))%>%
  mutate(charge_diff = c(0,diff(out_df$SoC, lag = 1)))%>%
  mutate(seas = getSeason(date_time))-> res_df

price_df %>%
  melt(id.vars = 'date_time', variable.name = 'product',value.name = 'price')%>%
  mutate(price = replace_na(price,0))-> price_res
  
```

# Pricing
- Distribution of pricing by month, day, day of week
```{r, fig.height=20, fig.width=30, message = FALSE, warning = FALSE}
weird <- scales::trans_new("signed_log",
       transform=function(x) sign(x)*log1p(abs(x)),
       inverse=function(x) sign(x)*expm1(abs(x)))

price_res%>%
  filter(product!= 'i' & product!= 'DAi' & product!= 'c' & product!= 'DAc')%>%
  mutate(product = fct_reorder(.f = product, .x = price))%>%
ggplot(aes(x = price, y = product, fill = product))+
  geom_density_ridges(scale = 2, linwidth = 2)+
  scale_x_continuous(trans=weird, 
                     breaks = c(-1000,-100,-10, 0,10,100,1000), limits = c(-1000,1000))+
  theme_ridges() + theme(legend.position = 'none')+
  facet_wrap(~month(date_time),ncol = 6)
```
```{r}
price_res%>%
  filter(product %in% c('d','DAd'), price > 0)%>%
  mutate(seas = factor(getSeason(date_time), levels = c('Spring','Summer','Fall','Winter')),
         isDA = if_else(str_detect(product,'DA'), 'DA','RT'))%>%
  ggplot(aes(x = seas, y = price))+
  stat_boxplot()+theme_bw()+facet_wrap(~isDA)+
  scale_y_log10(labels = dollar_format())+
    labs(title = 'Seasonal spread of positive RT/DALMP prices in the market',
         x = element_blank(), y = 'Price')-> p
p
ggsave(paste0(graph_path,'seasonal_boxes.png'),p)
```
```{r}
price_res%>%
  filter(product %in% c('d','DAd'), price > 0)%>%
  mutate(seas = factor(getSeason(date_time), levels = c('Spring','Summer','Fall','Winter')))%>%
  select(seas, price)->box_plot_price
vals <- boxplot(price~seas,box_plot_price)
temp <- data.frame(seas = vals$group,outlier = vals$out)

temp%>%
  group_by(seas)%>%
  summarise(seas_out_means = mean(outlier))
temp%>%
  mutate(seas = recode(seas, `1`='Spring', `2` = 'Summer', `3`='Fall', `4`='Winter' ))%>%
ggplot(aes(x = outlier))+
  geom_histogram(bins = 15)+facet_wrap(~seas)+theme_bw()+
  labs(title = 'Summer 2022 did not have a lot of high value outliers in price',
       x = 'Outlier Prices',y = 'Frequency')->p
  p
  ggsave(paste0(graph_path,'seasonal_outs.png'),p)
```

# Revenue
- Which model earned the most on the battery asset? By Month? By product?

## By Month

```{r}
graph_path <- 'C:\\Users\\brend\\Documents\\dev\\bss\\2022_study\\graphs\\'
res_df %>% 
  group_by(interval,mnth = month(date_time)) %>%
  summarise(earnings = sum(price))%>%
   ggplot(aes(x = factor(mnth), y = earnings, fill = interval))+
   geom_col(position = position_dodge()) +
  scale_y_continuous(labels = dollar_format())+
  labs(x = 'Month', y = 'Total Earnings', title = '2022 Total Earnings by Month (DA + RT + ANC)', fill= 'Planning Window') + 
  #scale_fill_discrete(labels = c('Hourly', '5 Minute'))+
  theme_bw()-> p
p
ggsave(paste0(graph_path,'rev_by_month.png'),p)
```
```{r}
res_df %>% 
  group_by(mnth = month(date_time),interval) %>%
  summarise(earnings = sum(price))%>%
  mutate(lag = lag(earnings))%>%
  mutate(pct.change = (earnings - lag)/lag,
         earnings_diff = earnings - lag)%>%
  filter (!is.na(lag))-> pct_earn
```


## By Month and Product
```{r}
my_colors <- brewer.pal(7, 'Paired')
RT_colors <- c(c = my_colors[1], d = my_colors[2], i = my_colors[7],
               regd = my_colors[3], regu = my_colors[4], spinr = my_colors[5],suppr = my_colors[6])
DA_colors <- c(DAc = my_colors[1], DAd = my_colors[2], DAi = my_colors[7],
               DAregd = my_colors[3], DAregu = my_colors[4], DAspinr = my_colors[5],DAsuppr = my_colors[6])


res_df %>% filter(isDA == 'DA')%>%
  group_by(interval,mnth = factor(month(date_time)),product) %>%
  summarise(earnings = sum(price))%>%
   ggplot(aes(x = mnth, y = earnings, fill = product))+
   geom_col()+facet_wrap(~interval)+ylim(-4e4,3e5)+scale_fill_manual(values = DA_colors)+
  scale_y_continuous(labels = dollar_format())+
  labs(x = 'Month', y = 'Earnings', title = '2022 DA Market Breakdown by Month', fill = 'Product') -> p1
p1
ggsave(paste0(graph_path,'DA_earn_byprod.png'),p1)

res_df %>% filter(isDA == 'not DA')%>%
  group_by(interval,mnth = factor(month(date_time)),product) %>%
  summarise(earnings = sum(price))%>%
   ggplot(aes(x = mnth, y = earnings, fill = product))+
   geom_col()+facet_wrap(~interval)+ylim(-4e4,3e5)+ scale_fill_manual(values = RT_colors)+
  scale_y_continuous(labels = dollar_format())+
  labs(x = 'Month', y = 'Earnings', title = '2022 RT Market Breakdown by Month', fill = 'Product') -> p2
p2
ggsave(paste0(graph_path,'RT_earn_byprod.png'),p2)

res_df %>% mutate(product = str_replace(product,'DA',''))%>%
  group_by(interval,mnth = factor(month(date_time)),product) %>%
  summarise(earnings = sum(price))%>%
   ggplot(aes(x = mnth, y = earnings, fill = product))+
   geom_col()+facet_wrap(~interval)+scale_fill_manual(values = RT_colors)+
  scale_y_continuous(labels = dollar_format())+
  labs(x = 'Month', y = 'Total Earnings', title = '2022 Total Earnings Breakdown by Month', fill = 'Product') -> p3
p3
ggsave(paste0(graph_path,'all_earn_byprod.png'),p3)
```
# By Weekday
```{r}
res_df %>% filter(isDA == 'DA')%>%
  group_by(interval,weekday = wday(date_time,label = TRUE),product) %>%
  summarise(earnings = sum(price))%>%
   ggplot(aes(x = weekday, y = earnings, fill = product))+
  ylim(-1.2e4,4e5)+scale_fill_manual(values = DA_colors)+
   geom_col()+facet_wrap(~interval)+
  scale_y_continuous(labels = dollar_format())+
  labs(x = NA, y = 'Earnings', title = '2022 DA Market Breakdown by Weekday', fill = 'Product')

res_df %>% filter(isDA == 'not DA')%>%
  group_by(interval,weekday = wday(date_time,label = TRUE),product) %>%
  summarise(earnings = sum(price))%>%
   ggplot(aes(x = weekday, y = earnings, fill = product))+ylim(-1.2e4,4e5)+
  scale_fill_manual(values = RT_colors)+
   geom_col()+facet_wrap(~interval)+
  scale_y_continuous(labels = dollar_format())+
  labs(x = element_blank(), y = 'Earnings', title = '2022 RT Market Breakdown by Weekday', fill = 'Product')

res_df %>% mutate(product = str_replace(product,'DA',''))%>%
  group_by(interval,weekday = wday(date_time,label = TRUE),product) %>%
  summarise(earnings = sum(price))%>%
   ggplot(aes(x = weekday, y = earnings, fill = product))+scale_fill_manual(values = RT_colors)+
   geom_col()+facet_wrap(~interval)+
  scale_y_continuous(labels = dollar_format())+
  labs(x = element_blank(), y = 'Total Earnings', title = '2022 Total Earnings Breakdown by Weekday', fill = 'Product') -> p
p
ggsave(paste0(graph_path,'all_earn_byprodbywkday.png'),p)
```

### Seasonality


```{r}
res_df%>%
  mutate(product = str_replace(product,'DA',''),
         seas = factor(seas, levels = c('Spring','Summer','Fall','Winter')))%>%
  group_by(interval, product,seas)%>%
  summarise(earnings = sum(price))%>%
  ggplot(aes(x = seas, y = earnings, fill = product))+
  geom_col()+facet_wrap(~interval)+theme_bw()+
  scale_y_continuous(labels = dollar_format())+
  labs(title = '2022 Total Earnings Breakdown by Season',
       x = element_blank(), y = 'Total Earnings')-> p

p
ggsave(paste0(graph_path,'seasonal_earnings.png'),p)
```

```{r}
for (s in unique(res_df$seas)) {
  

  # res_df %>% filter(isDA == 'DA' & seas == s)%>%
  #   group_by(interval,weekday = wday(date_time,label = TRUE),product) %>%
  #   summarise(earnings = sum(price))%>%
  #    ggplot(aes(x = weekday, y = earnings, fill = product))+
  #    geom_col()+facet_wrap(~interval)+ labs(title = paste(s,'DA')) -> p1
  # print(p1)
  # 
  # res_df %>% filter(isDA == 'not DA'& seas == s)%>%
  #   group_by(interval,weekday = wday(date_time,label = TRUE),product) %>%
  #   summarise(earnings = sum(price))%>%
  #    ggplot(aes(x = weekday, y = earnings, fill = product))+
  #    geom_col()+facet_wrap(~interval)+ labs(title = paste(s,'not DA')) -> p2
  # print(p2)
  
  res_df %>% filter(seas == s)%>%
    mutate(product = str_replace(product,'DA',''))%>%
    group_by(interval,weekday = wday(date_time,label = TRUE),product) %>%
    summarise(earnings = sum(price))%>%
     ggplot(aes(x = weekday, y = earnings, fill = product))+
    scale_fill_manual(values = RT_colors)+
     geom_col()+facet_wrap(~interval)+ 
    scale_y_continuous(labels = dollar_format())+
    labs(x = element_blank(), y = 'Total Earnings',title = paste(s, 'months Total Earnings'))-> p3
    print(p3)
ggsave(paste0(graph_path,s,'all_earn_byprodbywkday.png'),p3)
}
```
# Hourly Breakdown

```{r}
# res_df%>% filter(isDA == 'DA')%>%
#   filter(month(date_time)!= 2)%>%
#     group_by(interval,hr = hour(date_time),product) %>%
#     summarise(earnings = sum(price))%>%
#     ggplot(aes(x = factor(hr), y = earnings, fill = product))+
#   scale_y_continuous(labels = dollar_format())+
#   scale_fill_manual(values = DA_colors)+
#      geom_col()+facet_wrap(~interval)+
#   labs(x = 'Hour of day', y = 'Earnings',title = '2022 DA Earnings by Hour of Day')+theme_bw()+
#   theme(axis.text.x = element_text(angle = -30, hjust = 1))
# 
# res_df%>% filter(isDA == 'not DA')%>%
#   filter(month(date_time)!= 2)%>%
#     group_by(interval,hr = hour(date_time),product) %>%
#     summarise(earnings = sum(price))%>%
#     ggplot(aes(x = factor(hr), y = earnings, fill = product))+
#   scale_y_continuous(labels = dollar_format())+
#   scale_fill_manual(values = RT_colors)+
#      geom_col()+facet_wrap(~interval)+
#   labs(x = 'Hour of day', y = 'Earnings',title = '2022 RT Earnings by Hour of Day')+theme_bw()+
#   theme(axis.text.x = element_text(angle = -30, hjust = 1))

res_df%>%mutate(product = str_replace(product,'DA',''))%>%
  filter(month(date_time)!= 2)%>%
    group_by(interval,hr = hour(date_time),product) %>%
    summarise(earnings = sum(price))%>%
    ggplot(aes(x = factor(hr), y = earnings, fill = product))+
  scale_y_continuous(labels = dollar_format())+
  scale_fill_manual(values = RT_colors)+
     geom_col()+facet_wrap(~interval)+
  labs(x = 'Hour of day', y = 'Total Earnings',title = '2022 Total Earnings by Hour of Day')+theme_bw()+
  theme(axis.text.x = element_text(angle = -30, hjust = 1))
```

```{r, warning= FALSE}
for (m in unique(month(res_df$date_time))) {
#   res_df%>% filter(isDA == 'DA' & month(date_time) == m)%>%
#     group_by(interval,hr = hour(date_time),product) %>%
#     summarise(earnings = sum(price))%>%
#     ggplot(aes(x = factor(hr), y = earnings, fill = product))+
#      geom_col()+facet_wrap(~interval)+ labs(title = paste('DA month',m)) -> p1
#   print(p1)
# 
# res_df%>% filter(isDA == 'not DA'& month(date_time) == m)%>%
#     group_by(interval,hr = hour(date_time),product) %>%
#     summarise(earnings = sum(price))%>%
#     ggplot(aes(x = factor(hr), y = earnings, fill = product))+
#      geom_col()+facet_wrap(~interval)+ labs(title = paste('not DA month',m))-> p2
#   print(p2)

res_df%>%filter(month(date_time) == m)%>%
  mutate(product = str_replace(product,'DA',''))%>%
    group_by(interval,hr = hour(date_time),product) %>%
    summarise(earnings = sum(price))%>%
    ggplot(aes(x = factor(hr), y = earnings, fill = product))+
     geom_col()+facet_wrap(~interval)+ labs(title = paste('month',m)) ->p3
  print(p3)
}
```

# DA Market Participation
- Which products see the most usage across which time intervals?
- Which interval has the most day ahead participation? Which is making more money in the DA?


```{r}
res_df %>% filter(isDA == 'not DA')%>%
ggplot(aes(x = fct_infreq(product), fill = interval))+
  geom_bar()

res_df %>% filter(isDA == 'DA')%>%
ggplot(aes(x = fct_infreq(product), fill = interval))+
  geom_bar()

res_df %>% mutate(product = str_replace(product,'DA',''))%>%
ggplot(aes(x = fct_infreq(product), fill = interval))+
  geom_bar()+ facet_wrap(~isDA,ncol = 1)

res_df %>% mutate(product = str_replace(product,'DA',''))%>%
ggplot(aes(x = fct_infreq(product), fill = isDA))+
  geom_bar()+facet_wrap(~interval)
```
switch these to proportions 


```{r}
res_df %>%
  group_by(interval,isDA)%>%
  summarise(participation = n(), earnings = sum(price)) -> DA_summary

DA_summary$isDA[DA_summary$isDA == 'not DA'] <- 'RT'

DA_summary%>%
  group_by(interval)%>%
  mutate(part_proportion = participation/sum(participation))%>%
ggplot(aes(x = interval, y = part_proportion, fill = isDA))+
  geom_col()+
  scale_y_continuous(labels = scales::percent_format())+ theme_bw()+
  labs(x = 'Planning Window', y ='Real time vs Day Ahead Market Participation', fill = 'DA vs RT',
       title = '2022 Proportion of participation in DA and RT Markets') -> p1

ggsave(paste0(graph_path,'DA_participation_prop.png'),p1)

DA_summary%>%
  group_by(interval)%>%
  mutate(earn_proportion = earnings/sum(earnings))%>%
ggplot(aes(x = interval, y = earn_proportion, fill = isDA))+
  geom_col()+
  scale_y_continuous(labels = scales::percent_format())+ theme_bw()+
  labs(x = 'Planning Window', y ='Real time vs Day Ahead Earnings Proportion', fill = 'DA vs RT',
       title = '2022 Proportion of earnings in DA and RT Markets') -> p2

ggsave(paste0(graph_path,'DA_earnings_prop.png'),p2)

```

Real time spends less time in DA and earns less in DA (and visa versa)

# State of Charge

- Highlight where the models made different decisions

```{r, fig.height = 10, fig.width=15}
for(m in unique(month(res_df$date_time))){
res_df %>%
  filter(month(date_time) == m)%>%
  mutate(product = str_replace(product,'DA',''))%>%
  ggplot(aes(x = date_time, y = SoC, color = product))+
  geom_point(size = 1)+facet_wrap(~interval,ncol = 1)+theme_bw()+
    scale_y_continuous(labels = scales::percent_format())+
    labs(title = paste(year,'month',m,'State of Charge Over Time'),
         x = element_blank(),y = 'SoC')-> p
  print(p)
  ggsave(paste0(graph_path,'SoC\\',m,'soc.png'),p)
}
```
```{r}
start_date <- as.Date('2022-07-10')
end_date <- as.Date('2022-07-17')

res_df %>%
  filter(date_time >= start_date, date_time < end_date)%>%
  mutate(product = str_replace(product,'DA',''))%>%
  ggplot(aes(x = date_time, y = SoC, color = product))+
  geom_point(size = 1)+facet_wrap(~interval,ncol = 1)+theme_bw()+
    scale_y_continuous(labels = scales::percent_format())+
  scale_x_datetime(date_breaks = '1 day')+
    labs(title = paste('Reg Down is often profitable closer to midnight'),
         x = element_blank(),y = 'SoC')-> p
p
ggsave(paste0(graph_path,'202207_week_snapshot.png'),p)
```

```{r, fig.height = 10, fig.width=15}
for(m in unique(month(res_df$date_time))){
res_df %>%
  filter(month(date_time) == m)%>%
  mutate(product = str_replace(product,'DA',''),
         isDA = str_replace(isDA,'not DA','RT'))%>%
  ggplot(aes(x = date_time, y = SoC, color = isDA))+
  geom_point()+facet_wrap(~interval,ncol = 1)+theme_bw()+
    scale_y_continuous(labels = scales::percent_format())+
    labs(title = paste('Charge in the RT, Discharge in the DA'),
         x = element_blank(),y = 'SoC', color = 'DA or RT') -> p
  print(p)
  ggsave(paste0(graph_path,'SoC\\',m,'DA_soc.png'),p)
}
```
```{r}
cod <- function(v){
  if(v %in%  c('c','DAc','regd','DAregd')){return(1)}
  else if (v %in% c('i','DAi')){return(0)}
  else{return(-1)}
}
res_df$cod <- sapply(res_df$product, cod)
  
```

```{r}
res_df%>%filter(cod != 0,interval=='5-Minute')%>%mutate(isDA = str_replace(isDA,'not DA','RT')) -> temp_df1
res_df%>%filter(cod != 0,interval=='Hourly')%>%mutate(isDA = str_replace(isDA,'not DA','RT')) -> temp_df2
table(temp_df1$isDA,temp_df1$cod)
table(temp_df2$isDA,temp_df2$cod)
```
# Mileage

```{r}
res_df%>%
  group_by(interval,mnth = month(date_time))%>%
  summarise(tot_mileage = 4*sum(abs(charge_diff)))%>%
  ggplot(aes(x = factor(mnth), y = tot_mileage, fill = interval))+
  geom_col(position = position_dodge())+
  labs(title = '5-minute planning window will increase activity on the battery',
       x = 'Month', y = 'Hours of activity')+theme_bw() -> p
ggsave(paste0(graph_path,'mileage_by_month.png'),p,
       width = 10, height = 7)
```
```{r}
res_df%>%
  group_by(interval,mnth = month(date_time))%>%
  summarise(tot_mileage = 4*sum(abs(charge_diff)))%>%view()
```


# RT vs Hourly Differences in schedule

```{r}
res_df %>% select(date_time,interval,product)%>%
dcast(date_time ~ interval, value.var = c('product'))%>%
mutate(diff = (`5-Minute` == Hourly))->df_comp
#df_comp <- data.table::dcast(res_df,date_time ~ interval,value.var = 'product')
#df_comp2 <- reshape(res_df, idvar = 'date_time', timevar = 'interval', direction = 'wide')
```

```{r}
res_df %>%
  filter(interval == '5-Minute')%>%
  inner_join(df_comp)->res_df_rt
```
```{r}
for(m in unique(month(res_df_rt$date_time))){
res_df_rt %>%
  filter(month(date_time) == m)%>%
  ggplot(aes(x = date_time, y = SoC, color = diff))+
  geom_point()+facet_wrap(~interval,ncol = 1) -> p
  print(p)
}
```

```{r}
res_df_rt%>%
  filter(diff == FALSE)%>%
  group_by(Hourly)%>%
  summarise(hourly_state_diff = n())%>%
  ggplot(aes(x = fct_reorder(Hourly,hourly_state_diff), y = hourly_state_diff))+
  geom_col()


res_df_rt%>%
  filter(diff == FALSE)%>%
  group_by(`5-Minute`)%>%
  summarise(realtime_state_diff = n())%>%
  ggplot(aes(x = fct_reorder(`5-Minute`,realtime_state_diff), y = realtime_state_diff))+
  geom_col()+labs(title = 'Product switched to in 5-minute window',x = 'Market Product', y = 'Count')+theme_bw()->p1
p1
ggsave(paste0(graph_path,'rt_switch_decisions.png'),p1,
              width = 6, height = 2)

res_df_rt%>%
  filter(diff == FALSE)%>%
  group_by(Hourly,`5-Minute`)%>%
  summarise(f = n())%>%
  ggplot(aes(x=`5-Minute`,y=Hourly))+
  geom_tile(aes(fill = f)) + scale_fill_gradient(low = 'light pink', high = 'red')+theme_minimal()+
  labs(x = 'Product chosen in the 5-minute window instead', y='Product decision in the hourly planning window', title = 'The 5-minute window often prefers the Real Time ancillary services', fill = 'Frequency')->p2

p2
ggsave(paste0(graph_path,'decision_heatmap.png'),p2)
```


```{r}
group_by(price_df,date_time)%>%
  summarise(ct = n())%>%
  filter(ct >1)
```

